---
title: "Hands_on_sessions_10"
author: "Janet Piñero (janet.pinero@upf.edu)"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"      
output:
  html_document:
    toc: true
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Exercise 1

You will download a subset of [MIMIC III](https://www.nature.com/articles/sdata201635) data from the campus global. The data contains only the hospital admission data. The only preprocessing that has been done is changing the column names and removing the information for  ~ 8,000 neonates admitted between 2001 and 2008 that had no further information. 
```{r}
library(data.table)
codes <- fread("data/allDiseaseCodes.txt", quote = "")

```


# EDA

Perform an EDA for the data. 
Some guide questions for the EDA are:

What are the most prevalent diseases? Are they different is data is stratified by gender? 
What are the most prevalent diseases when aggregating codes to the level of chapters?
## top diseases in the dataset

### top diseases by gender

# Comorbidities of Obesity

What are the diseases that co-occur with obesity?   
Hint: use the field “Description” in the codes file to retrieve the ICD 9 codes containing the string “obesity”  
```{r}
subset(codes, grepl("obesity", tolower(Description)))

```

Alternatively, use the corresponding ICD 9 code. Important note: for these data, the dot of the ICD-9 code has been removed 

## Comorbidities of Obesity stratified by gender

Are the same comorbidities occurring in men and in women ?  


Present the results in a publication-like manner: appropriately use tables and/or different types of plots
Are there any of the comorbidities supported by the literature? Do they have common genetic basis?


```{r}

```

# session info {.unnumbered}

```{r, results='asis',  echo=FALSE, message=FALSE }
sessionInfo()
```
